### 2016-08-31 syntax.tex
syntax

\heading{Data structures.}  We being by defining a general primitive
that produces a representation of a given multiset, and provides a
mechanism to answer a specified collection of questions about that
multiset.
%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix a non-empty set~$\univ$, and a set of multisets~$\calS$ over
$\univ$. 
A \emph{data structure} (for $\calS$) is a tuple $\setprim=(\calQ,\Rep, \Qry)$ where:
\begin{itemize}
\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set
    of supported \emph{queries}, where $\Gamma$ is the set of query \emph{answers}.
\item $\Rep \colon \mathcal{S} \to \bits^*
    \times \bits^*$ is a randomized \emph{representation
    algorithm}, taking as input $S \in \mathcal{S}$, and
    outputting a \emph{representation} $M \in \Sigma^*$,
    \emph{private side information} $\privaux \in \bits^*$, and
    \emph{public side information} $\pubaux \in \bits^*$.  We write
    $(M,\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
\item $\Qry\colon \Sigma^* \times \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $M\in\Sigma^*$, $\pubaux,\privaux \in
    \bits^*$ and $q \in \calQ$, and outputting
    an \emph{answer} $a \in \Gamma$.  We write $a \gets
    \Qry(M,\pubaux,\privaux,q)$ for this execution.
\end{itemize}
\hfill\dqed
\end{definition}
%\tsnote{I implemented this change.}\tsnote{I'm now leaning towards
%having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
%Pushing secrets into~$M$ makes it more difficult to capture (for
%example) the Neidermeier et al.\ attacks in our privacy notions; see
%Figure~\ref{fig:privacy}.  In those attacks, the adversary would get
%the bitarray (which one naturally thinks of as~$M$) but not the
%secret keys for the PRFs/hash functions.  You could say that the
%bitarray is put in $\aux$ and that~$M$ \emph{only} contains the
%secret keys, but this is unnatural.}
All of the data structures that
we will consider have the property that~$|M|$ does not depend on the
coins of~$\Rep$. Thus we assume that~$|M|$ depends only on~$|S|$. In
general this need not be true, but the assumption does not restrict
our syntax from capturing natural constructions (e.g., those used in
practice), and it makes it easier to state our security notions.

\jnote{I think we agreed to just have the syntax output $(\pub, \privaux)$, with
the semantics being that in our definitions $\pub$ is always
  public and $\privaux$ is always private.
  Different schemes can then choose whether $M$ is in $\pub$
  or $\privaux$. If we do this, then need to be careful how to define size, though
  I don't think we ever explicitly care about size for any of our results.}

>>>>

\heading{Data structures.}  We being by defining a general primitive
that produces a representation of a given multiset, and provides a
mechanism to answer a specified collection of questions about that
multiset.
%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix a non-empty set~$\univ$, and a set of multisets~$\calS$ over
$\univ$. 
A \emph{data structure} (for $\calS$) is a tuple $\setprim=(\calQ,\Rep, \Qry)$ where:
\begin{itemize}
\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set
    of supported \emph{queries}, where $\Gamma$ is the set of query \emph{answers}.
\item $\Rep \colon \mathcal{S} \to \bits^*
    \times \bits^*$ is a randomized \emph{representation
    algorithm}, taking as input $S \in \mathcal{S}$, and outputting %a \emph{representation} $M \in \Sigma^*$,
    \emph{private representation data} $\privaux \in \bits^*$, and
    \emph{public representation data} $\pubaux \in \bits^*$.  We write
    $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
\item $\Qry\colon \Sigma^* \times \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $\pubaux,\privaux \in
    \bits^*$ and $q \in \calQ$, and outputting
    an \emph{answer} $a \in \Gamma$.  We write $a \gets
    \Qry(\pubaux,\privaux,q)$ for this execution.
\end{itemize}
\hfill\dqed
\end{definition}

\todo{Insert discussion of syntax, if needed.  If we think it is
  helpful to discuss the size of the representation, we can declare it
as $|\pubaux|+|\privaux|$ and comment that if one wants to compare to
classical size bounds, a more fine-grained separation of the output of
$\Rep$ would allow this.}
%\tsnote{I implemented this change.}\tsnote{I'm now leaning towards
%having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
%Pushing secrets into~$M$ makes it more difficult to capture (for
%example) the Neidermeier et al.\ attacks in our privacy notions; see
%Figure~\ref{fig:privacy}.  In those attacks, the adversary would get
%the bitarray (which one naturally thinks of as~$M$) but not the
%secret keys for the PRFs/hash functions.  You could say that the
%bitarray is put in $\aux$ and that~$M$ \emph{only} contains the
%secret keys, but this is unnatural.}

%All of the data structures that we will consider have the property that~$|M|$ does not depend on the
%coins of~$\Rep$. Thus we assume that~$|M|$ depends only on~$|S|$. In
%general this need not be true, but the assumption does not restrict
%our syntax from capturing natural constructions (e.g., those used in
%practice), and it makes it easier to state our security notions.

%\jnote{I think we agreed to just have the syntax output $(\pub, \privaux)$, with
%the semantics being that in our definitions $\pub$ is always
%  public and $\privaux$ is always private.
%  Different schemes can then choose whether $M$ is in $\pub$
%  or $\privaux$. If we do this, then need to be careful how to define size, though
%  I don't think we ever explicitly care about size for any of our results.}
